Verifying Demonstrations

### 2019-09-06 paper/DB-anon-cred.tex
Concurrent ZK is not an issue
Concurrent ZK is a prover running parallel sessions with multiple
verifiers --- our situation is one verifier with multiple provers.
Removes discussion about negligible for MF resistance

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields a success with probability 
    \(\frac{1}{k}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}

  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
  thus \((q + k)^n (kq)^{-n}\) in total.
  We have that \(k \in \log(\lambda)\), \(q \in \poly[\lambda]\) and it follows 
  that the success probability is negligible,
  \[
    \left( \frac{\log(\lambda) + 
        \poly[\lambda]}{\log(\lambda)\poly[\lambda]}\right)^n \approx
    \frac{1}{\log(\lambda)^n} < \frac{1}{\poly[\lambda]}
  \] for \(n > 2\).
\end{proof}

@@

\begin{proof}
  The adversary must find a collision of challenges for the honest prover's 
  challenges, so that the verifying equation holds at the end.
  Let \(R, c_1, \dotsc, c_k\) be the transcript of the setup between the honest 
  verifier and the adversary.
  Let \(R', c_1', \dotsc, c_k'\) be the transcript of the setup between the 
  honest verifier and honest prover.
  The verifier will accept if \(R = g^{s_i'} A^{c_i}\), where \(s_i' = \rho' - 
    c_i'\alpha'\) is the response by the honest prover computed for his 
  session, \ie \(\rho = \rho' - c_i'\alpha' + c_i\alpha\).
  Since the verifier and prover are honest, \(\rho', c_i'\), \(\alpha'\) and 
  \(c_i\) are chosen uniformly randomly.
  \(\alpha\) is also chosen uniformly randomly and is fixed.

  \daniel{\Ac{DBDH} is kind of adaptive and concurrent \ac{ZKPK}, I must read 
    up on that (there is a paper by Bellare).}
\end{proof}

>>>>

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields a success with probability 
    \(\frac{1}{k}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}
  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
  thus \[\left(\frac{1}{k}+\frac{1}{q}\right)^n = (q + k)^n (kq)^{-n}\] in 
  total per protocol session.
\end{proof}

@@

\begin{proof}
  The adversary must find a collision of challenges for the honest prover's 
  challenges, so that the verifying equation holds at the end.
  Let \(R, c_1, \dotsc, c_k\) be the transcript of the setup between the honest 
  verifier and the adversary.
  Let \(R', c_1', \dotsc, c_k'\) be the transcript of the setup between the 
  honest verifier and honest prover.
  The verifier will accept if \(R = g^{s_i'} A^{c_i}\), where \(s_i' = \rho' - 
    c_i'\alpha'\) is the response by the honest prover computed for his 
  session, \ie \(\rho = \rho' - c_i'\alpha' + c_i\alpha\).
  Since the verifier and prover are honest, \(\rho', c_i'\), \(\alpha'\) and 
  \(c_i\) are chosen uniformly randomly.
  \(\alpha\) is also chosen uniformly randomly and is fixed.
\end{proof}
